---
title: "gtsummary in quarto"
format: 
  html: 
    theme: quartz
#EXERCISE: Play around with theme!! two spaces- it needs to be exact
#EXERCISE 4: Let’s not print the code from creating the tables. Using an option for the whole document, make it so that we don’t see the code from any of the chunks.
execute: 
  echo: false 
  
 #i want to keep echo false- it is a cleaner look
  
 #to make the gtsummary tables colorful, use the following. it removes the indents though. 
 #as kable: true
---

```{r}
# EXERCISE 3: I don’t like seeing the output from the first chunk, where the packages are loaded. Use an option that makes it so that we don’t see this chunk’s output. Add Message : false

#| message: false 
#| echo: true
library(tidyverse)
library(gtsummary)
nlsy_cols <- c("glasses", "eyesight", "sleep_wkdy", "sleep_wknd", 
               "id", "nsibs", "samp", "race_eth", "sex", "region", 
               "income", "res_1980", "res_2002", "age_bir")
nlsy <- read_csv(here::here("data", "raw", "nlsy.csv"), 
                 na = c("-1", "-2", "-3", "-4", "-5", "-998"),
                 skip = 1, col_names = nlsy_cols) |> 
  mutate(region_cat = factor(region, labels = c("Northeast", "North Central", "South", "West")),
         sex_cat = factor(sex, labels = c("Male", "Female")),
         race_eth_cat = factor(race_eth, labels = c("Hispanic", "Black", "Non-Black, Non-Hispanic")),
         eyesight_cat = factor(eyesight, labels = c("Excellent", "Very good", "Good", "Fair", "Poor")),
         glasses_cat = factor(glasses, labels = c("No", "Yes"))) 
```

# Customization of `tbl_summary()`

```{r}
tbl_summary(
  nlsy,
  by = sex_cat,
  include = c(sex_cat, race_eth_cat, region_cat,
              eyesight_cat, glasses, age_bir))
```

```{r}
tbl_summary(
  nlsy,
  by = sex_cat,
  include = c(sex_cat, race_eth_cat, region_cat,
              eyesight_cat, glasses, age_bir),
  label = list(
    race_eth_cat ~ "Race/ethnicity",
    region_cat ~ "Region",
    eyesight_cat ~ "Eyesight",
    glasses ~ "Wears glasses",
    age_bir ~ "Age at first birth"
  ),
  missing_text = "Missing")
```

EXERCISE SET 2:

```{r}
#| error: true
#| eval: true
tbl_summary(
  nlsy,
  by = sex_cat,
  include = c(sex_cat, race_eth_cat, region_cat,
              eyesight_cat, glasses, age_bir))

```

Great! So error true gave me an idea of what the error is. Here is the corrected code:

```{r}
tbl_summary(
  nlsy,
  by = sex_cat,
  include = c(sex_cat, race_eth_cat, region_cat,
              eyesight_cat, glasses, age_bir))
```

INLINE R
I want to add `r 3+4` participants
There were `r nrow(nlsy)` participants

but the spacing is weird, so to make the spacing right, need the double line 
INLINE R

I want to add `r 3+4` participants

There were `r nrow(nlsy)` participants

```{r}
#| label: tbl-one
#| tbl-cap: "This is the first  table"
knitr::kable(mtcars)
```
NEED TO RUN PREV CHUNKS for this to work!!!!!!!
```{r}
#| error: true
#| label: tbl-sex
#| tbl-cap: "descriptive statistics stratified by sex"

tbl_summary(
  nlsy,
  by = sex_cat,
  include = c(sex_cat, race_eth_cat, region_cat,
              eyesight_cat, glasses, age_bir))
```
DOne

The descriptive statistics are shown stratified by sex (@tbl-sex). 
```{r}

mean_sleep_weekend <- mean(nlsy$sleep_wknd, na.rm = TRUE) 
```

We need the na.rm function to get rid of any NAs
People slept an average of `r mean_sleep_weekend` hours

Regression tables with gt summary 
```{r}
stats <- list(n = nrow(nlsy),
              mean_age = mean(nlsy$age_bir, na.rm = TRUE))
```

There were `r stats$n` participants with a mean age of `r stats$mean_age`
```{r}
#| label: tbl-descr
#| tbl-cap: "Descriptive statistics"
#| output-location: slide
table_descriptive <- tbl_summary(
  nlsy,
  by = sex_cat,
  include = c(sex_cat, race_eth_cat, region_cat,
              eyesight_cat, glasses, age_bir)) |> 
  add_overall(last = TRUE)
table_descriptive
```

needed the table summary above to make it work
```{r}
inline_text(table_descriptive, variable = "age_bir", column = "stat_1")
```
```{r}
inline_text(table_descriptive, variable = "glasses", column = "stat_0",
            pattern = "{n}/{N} ({p}%)")
```
| error: TRUE 

wont work, because this isnt a regression table. so lets redo it with a regression table. 
inline_text(table_descriptive, variable = "age_bir",




